Construction of Chebyshev nets with singularities

### 2017-07-06 Article.tex
Ajout du chapitre 5

\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{float}
\usepackage{tikz}

\usetikzlibrary{calc}

@@

@@

@@

@@

@@

\begin{center}{Y.~Masson$^{\textrm{1}}$,
    A.~Ern$^{\textrm{1}}$, L.~Hauswirth$^{\textrm{2}}$,
    L.~Monasse$^{\textrm{1}}$} \end{center}
\begin{center}
  $^{\textrm{1}}$ Universit\'e Paris-Est, CERMICS (ENPC), \\
  6 et 8 avenue Blaise Pascal, Cit\'e Descartes, Champs sur Marne, 77455, Marne la Vall\'ee, Cedex 2, France.
\end{center}
\begin{center}
  $^{\textrm{1}}$ Universit\'e Paris-Est, LAMA, \\
  5 boulevard Descartes, Cit\'e Descartes, Champs sur Marne, 77455, Marne la Vall\'ee, Cedex 2, France.
\end{center}

@@

@@

\begin{figure}[!ht]

@@

\begin{figure}[!ht]
  \centering
  \begin{tikzpicture}[x=2cm,y=2cm]
    \draw[red] (0,0) node[anchor=north east,inner sep=0pt]{$x(0)$};
    \draw[red] (0,0) node{$\times$};
    \draw[thick,red] (0,0) arc[start angle=110,delta angle=-40,radius=5] coordinate[pos=0.7] (v1) coordinate[pos=0.3] (v2);
    \draw[red] (v1) node[anchor=north]{$\varphi_\omega(\cdot,0){=}\gamma_{u}$};
    \draw[thick,red] (0,0) arc[start angle=200,delta angle=-40,radius=5] coordinate[pos=0.5] (v3);
    \draw[red] (v3) node[anchor=east]{$\varphi_\omega(0,\cdot){=}\gamma_{v}$};
    \draw (v2) arc[start angle=200,delta angle=-51,radius=3.5] coordinate[pos=0.4] (v4)  coordinate[pos=0.7] (v5);
    \draw (v4) node[anchor=east]{$\varphi_\omega(\eta,\cdot)$};
    \draw[red] (v2) node[anchor=north,inner sep=2pt]{$x(\eta)$};
    \draw[red] (v2) node{$\times$};
    \draw[-latex] (v2) -- ($(v2)+(8:.6)$) node[anchor=north west,pos=.3]{$\gamma_u'(\eta)$};
    \draw[-latex] (v2) -- ($(v2)+(110:.6)$) node[anchor=east, inner sep=0pt,pos=.6]{$V(\eta)$};
    \draw[-latex,red] ($(v2)+(8:0.3)$) arc[start angle=8,delta angle=102,radius=0.3];
    \draw[red] ($(v2)+(65:0.2)$) node[anchor=south west]{$\omega(\eta,0)$};
    \draw[red] ($(75:0.2)$) node[anchor=south west]{$\omega(0,0)$};
    \draw (v5) node[anchor=east]{$\varphi_\omega(\eta,s)$};
    \draw (v5) node{$\times$};
    \draw[-latex] (v5) -- ($(v5)+(73:.6)$) node[anchor=east]{$\partial_v\varphi_\omega(\eta,s)$};
    \draw[-latex] (v5) -- ($(v5)+(8:.6)$);
    \draw[-latex] ($(v5)+(8:0.3)$) arc[start angle=8,delta angle=65,radius=0.3];
    \draw ($(v5)+(35:0.25)$) node[anchor=south west]{$\omega(\eta,s)$};
    \draw[-latex,red] ($(17:0.3)$) arc[start angle=17,delta angle=93,radius=0.3];
  \end{tikzpicture}
  \caption{Illustration of the construction of the parametrization $\varphi_\omega$}\label{fig:construction2}
\end{figure}

@@

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{float}
\usepackage{tikz}
\usepackage{subcaption}

\usetikzlibrary{calc,decorations.markings,positioning,shapes,patterns, intersections,matrix,decorations.pathreplacing,quotes}

@@

 \newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}

@@

\newcommand{\psileft}{\psi^{\text{left}}}
\newcommand{\psiright}{\psi^{\text{right}}}
\newcommand{\sect}{Q}
\newcommand{\HalfP}{S}
\newcommand{\halfP}{B}
\newcommand{\cjunc}{\eta_{\text{junc}}}
\newcommand{\koin}{\ko_{\text{init}}}
\newcommand{\OO}{\mathcal{O}}
\newcommand{\psim}{|\psi|_{l^\infty}}
\newcommand{\psitot}{|\psi|_{l^1}}
\newcommand{\hmax}{h_{\max}}
\newcommand{\hmin}{h_{\min}}
\newcommand{\N}{\mathcal{N}}
\renewcommand{\S}{\mathcal{S}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\Nsing}{\mathcal{N}_{\mathrm{sing}}}
\newcommand{\Nver}{\mathcal{N}_{\mathrm{ver}}}
\newcommand{\Ned}{\mathcal{N}_{\mathrm{ed}}}
\newcommand{\Ndel}{\mathbf{N}}
\newcommand{\ndel}{\mathbf{n}}
\newcommand{\Npiece}{\mathcal{N}_{\mathrm{piece}}}
\newcommand{\phiband}{\varphi_{\mathrm{band}}}
\newcommand{\Bcband}{B_c^{\mathrm{band}}}
\newcommand{\Beband}{B_e^{\mathrm{band}}}
\newcommand{\NpolT}{\tilde{\mathcal{N}}_{\mathrm{pol}}}
\newcommand{\NpieceT}{\tilde{\mathcal{N}}_{\mathrm{piece}}}

\renewcommand{\H}{\mathcal{H}}
\newcommand{\Npol}{\mathcal{N}_{\mathrm{pol}}}

@@

\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{proprieteE}[theorem]{Property}
\newtheorem{problematiqueE}[theorem]{Issue}
\newtheorem{questionE}[theorem]{Question}
\newtheorem{corollaryE}[theorem]{Corollary}
\newtheorem{definitionE}[theorem]{Definition}

\theoremstyle{remark}
\newtheorem{exempleE}[theorem]{Example}
\newtheorem{remarkE}[theorem]{Remark}
\newtheorem{exempleF}[theorem]{Exemple}
\newtheorem{remarkF}[theorem]{Remarque}

@@

\makeatletter
\long\def\my@drawfill#1#2;{%
\@skipfalse
\fill[#1,draw=none] #2;
\@skiptrue
\draw[#1,fill=none] #2;
}

\newcommand{\drawfill}[1][]{%
  \my@drawfill{#1}}

\newif\if@skip

\newcommand{\skipit}[1]{%
\if@skip
\else
#1
\fi
}

\newcommand{\comment}[1]{}

@@

\begin{center}{Y.~Masson$^{\textrm{1}}$,
    A.~Ern$^{\textrm{1}}$, L.~Hauswirth$^{\textrm{2}}$,
    L.~Monasse$^{\textrm{1}}$} \end{center}
\begin{center}
  $^{\textrm{1}}$ Universit\'e Paris-Est, CERMICS (ENPC), \\
  6 et 8 avenue Blaise Pascal, Cit\'e Descartes, Champs sur Marne, 77455, Marne la Vall\'ee, Cedex 2, France.
\end{center}
\begin{center}
  $^{\textrm{2}}$ Universit\'e Paris-Est, LAMA, \\
  5 boulevard Descartes, Cit\'e Descartes, Champs sur Marne, 77455, Marne la Vall\'ee, Cedex 2, France.
\end{center}

@@

\textcolor{red}{DEBUT DU CHAPITRE 4}

@@

\begin{figure}[!htp]

@@

\begin{figure}[!htp]
  \centering
  \begin{tikzpicture}[x=2cm,y=2cm]
    \draw[red] (0,0) node[anchor=north east,inner sep=0pt]{$x(0)$};
    \draw[red] (0,0) node{$\times$};
    \draw[thick,red] (0,0) arc[start angle=110,delta angle=-40,radius=5] coordinate[pos=0.7] (v1) coordinate[pos=0.3] (v2);
    \draw[red] (v1) node[anchor=north]{$\varphi_\omega(\cdot,0){=}\gamma_{u}$};
    \draw[thick,red] (0,0) arc[start angle=200,delta angle=-40,radius=5] coordinate[pos=0.5] (v3);
    \draw[red] (v3) node[anchor=east]{$\varphi_\omega(0,\cdot){=}\gamma_{v}$};
    \draw (v2) arc[start angle=200,delta angle=-51,radius=3.5] coordinate[pos=0.4] (v4)  coordinate[pos=0.7] (v5);
    \draw (v4) node[anchor=east]{$\varphi_\omega(\eta,\cdot)$};
    \draw[red] (v2) node[anchor=north,inner sep=2pt]{$x(\eta)$};
    \draw[red] (v2) node{$\times$};
    \draw[-latex] (v2) -- ($(v2)+(8:.6)$) node[anchor=north west,pos=.3]{$\gamma_u'(\eta)$};
    \draw[-latex] (v2) -- ($(v2)+(110:.6)$) node[anchor=east, inner sep=0pt,pos=.6]{$V(\eta)$};
    \draw[-latex,red] ($(v2)+(8:0.3)$) arc[start angle=8,delta angle=102,radius=0.3];
    \draw[red] ($(v2)+(65:0.2)$) node[anchor=south west]{$\omega(\eta,0)$};
    \draw[red] ($(75:0.2)$) node[anchor=south west]{$\omega(0,0)$};
    \draw (v5) node[anchor=east]{$\varphi_\omega(\eta,s)$};
    \draw (v5) node{$\times$};
    \draw[-latex] (v5) -- ($(v5)+(73:.6)$) node[anchor=east]{$\partial_v\varphi_\omega(\eta,s)$};
    \draw[-latex] (v5) -- ($(v5)+(8:.6)$);
    \draw[-latex] ($(v5)+(8:0.3)$) arc[start angle=8,delta angle=65,radius=0.3];
    \draw ($(v5)+(35:0.25)$) node[anchor=south west]{$\omega(\eta,s)$};
    \draw[-latex,red] ($(17:0.3)$) arc[start angle=17,delta angle=93,radius=0.3];
  \end{tikzpicture}
  \caption{Illustration of the construction of the parametrization $\varphi_\omega$}\label{fig:construction2}
\end{figure}

@@

\textcolor{red}{DEBUT DU CHAPITRE 5}

\newsavebox\myboxa
\newsavebox\myboxb
\newsavebox\myboxc
\newsavebox\boxskeleton

\begin{lrbox}{\boxskeleton}
  \begin{tikzpicture}[x=0.7cm,y=1.cm]
    \pgfmathsetmacro{\R}{0.7}
    \pgfmathsetmacro{\RR}{1.4}
    \pgfmathsetmacro{\pos}{0.5}

    \coordinate (B) at (3,0);
    \coordinate (B2) at (14,0);

    \coordinate (C) at ($(B)+(0.66,2)$);
    \coordinate (C2) at ($(B)+(2.25,6.75)$);
    \coordinate (D) at ($(C)+(2,2)$);
    \coordinate (D2) at ($(C)+(5,5)$);
    \coordinate (E) at ($(D)+(5,1)$);
    \coordinate (E2) at ($(D)+(8.75,1.75)$);

    \draw (B) -- (B2) coordinate[pos=0.5] (BB) 
    node[pos=\pos,anchor=north west,inner sep=1pt]{$\gamma_c^{1,1}$};

    \coordinate (Z) at ($(BB)+(-1.,-3)$);
    \coordinate (Z2) at ($(BB)+(-2.,-6.)$);
    \coordinate (Y) at ($(Z)+(-9,-3)$);

    \draw[dashed] (B2) -- ($(B2)+(2.5,0)$);
    \draw (B) -- (C) node[pos=\pos,anchor=north west,inner sep=1pt]{$\gamma_c^{1,2}$};
    \draw (C) -- (C2) node[pos=.8,anchor=east,inner sep=1pt]{$\gamma_c^{3,3}$};
    \draw[dashed] (C2) -- ($(C2)+(0.5,1.5)$);
    \draw (C) -- (D) node[pos=\pos,anchor=west,inner sep=1pt]{$\gamma_c^{1,3}{=}\gamma_c^{3,2}$};
    \draw (D) -- (D2) node[pos=0.9,anchor=east,inner sep=3pt]{$\gamma_c^{2,2}{=}\gamma_c^{3,1}$};
    \draw[dashed] (D2) -- ($(D2)+(1,1)$);
    \draw (D) -- (E) node[pos=1.,anchor=north,inner sep=5pt]{$\gamma_c^{1,4}{=}\gamma_c^{2,1}$};
    \draw (E) -- (E2);
    \draw[dashed] (E2) -- ($(E2)+(2.,0.4)$);

    % \draw (10,4.3) node{\Large$\sect_{1,0}$};
    % \draw (11.5,4.3) node{\large$\sect^l_{1,1}$};
    % \draw (6.5,6.5) node{\large$\sect^r_{1,1}$};
    % \draw (11,6.5) node{$\sect^r_{1,2}$};
    % \draw (11,2.3) node{\large$\sect^l_{1,2}$};

  %  \draw (B) node[anchor=north east,inner sep=0pt]{$p_c^1$}; 
  %  \draw (C) node[anchor=north west,inner sep=0pt]{$p_c^2$}; 
  %  \draw (D) node[anchor=north west,inner sep=0pt]{$p_c^3$};

    \draw (B) node{$\times$};
    \draw (C) node{$\times$}; 
    \draw (D) node{$\times$};

    \draw (11.5,2.2) node{\large$\halfP_c^1$};

    \draw (6.,5.8) node{\large$\halfP_c^3$};
    \draw (12,6.8) node{\large$\halfP_c^2$};
  \end{tikzpicture}
\end{lrbox}

\begin{lrbox}{\myboxa}
  \begin{tikzpicture}
    \pgfmathsetmacro{\size}{2.5}
    \pgfmathsetmacro{\del}{0.65}
    \pgfmathsetmacro{\pos}{0.35}
    \pgfmathsetmacro{\poss}{0.75}
    \pgfmathsetmacro{\car}{0.25}

    \coordinate (O) at (0,0);
    \draw (O) node{$\times$}; 
    \draw (O) node[anchor=north east, inner sep=1pt]{\footnotesize$(0,0)$}; 
    \coordinate (A) at (0,\size);
    \coordinate (B) at (\size,0);
    % {\tiny$\backslash\backslash\backslash$}
    \draw (O) -- (A)% node[pos=\pos,anchor=east]{$p_e^{2,1}$}
    node[pos=\pos]{$\times$}  node[pos=\poss]{$\times$};
  %  node[pos=2.*\pos/3.,anchor=west, inner sep=0pt]{\small$\gamma_e^{2,1}$}
  %  node[pos=\poss,anchor=east]{$p_e^{3,1}$}
  %  node[pos=(\pos+\poss)/2.,sloped]{\scriptsize$\backslash$} 
  %  node[pos=0.95,sloped]{\scriptsize$\backslash\backslash$};
    \draw (O) -- (B);% node[pos=0.5,anchor=north]{\small$\gamma_e^{1,1}$};
    \draw[dashed] (B) -- ++(0:\del);
    \draw[dashed] (A) -- ++(90:\del);
    \draw (\size/2.+.3,\size/2.+.5) node{\large$\halfP^1_e$};
    \draw ($(O)+(0:\car)$) -- +(90:\car) -- (0,\car);
  \end{tikzpicture}
\end{lrbox}

\begin{lrbox}{\myboxb}
  \begin{tikzpicture}
    \pgfmathsetmacro{\size}{2.5}
    \pgfmathsetmacro{\del}{0.6}
    \pgfmathsetmacro{\pos}{0.4}
    \pgfmathsetmacro{\poss}{0.8}
    \pgfmathsetmacro{\car}{0.25}

    \coordinate (O) at (0,0);
    \draw (O) node{$\times$}; 
    \draw (O) node[anchor=north east, inner sep=1pt]{\footnotesize$(0,0)$}; 
    \coordinate (A) at (0,\size);
    \coordinate (B) at (\size,0);
    % {\tiny$\backslash\backslash\backslash$}
    \draw (O) -- (A);%  node[pos=(\pos+\poss)/2.,sloped]
%    {\scriptsize$\backslash\backslash\backslash$};
    \draw (O) -- (B);% node[pos=(\pos+\poss)/2.,sloped]
 %   {\scriptsize$\backslash\backslash$};
    \draw[dashed] (B) -- ++(0:\del);
    \draw[dashed] (A) -- ++(90:\del);

    \draw ($(O)+(0:\car)$) -- +(90:\car) -- (0,\car);

    \draw (\size/2.+.3,\size/2.+.5) node{\large$\halfP^2_e$};
  \end{tikzpicture}
\end{lrbox}

\begin{lrbox}{\myboxc}
  \begin{tikzpicture}
    \pgfmathsetmacro{\size}{2.5}
    \pgfmathsetmacro{\del}{0.65}
    \pgfmathsetmacro{\pos}{0.55}
    \pgfmathsetmacro{\car}{0.25}

    \coordinate (O) at (0,0);
    \draw (O) node{$\times$}; 
    \draw (O) node[anchor=north east, inner sep=1pt]{\footnotesize$(0,0)$}; 
    \coordinate (A) at (0,\size);
    \coordinate (B) at (\size,0);
    % {\tiny$\backslash\backslash\backslash$}
    \draw (O) -- (A); %node[pos=0.5,anchor=east, inner sep=0pt]{\small$\gamma_e^{6,1}$};
    \draw (O) -- (B) %node[pos=\pos,anchor=north]{$p_e^{3,3}$}
    node[pos=\pos]{$\times$};
  %  node[pos=\pos/2.,sloped]{\scriptsize$\backslash$} 
  %  node[pos=.5+\pos/2.,sloped]{\scriptsize$\backslash\backslash\backslash$};
    \draw[dashed] (B) -- ++(0:\del);
    \draw[dashed] (A) -- ++(90:\del);
    \draw (\size/2.+.3,\size/2.+.5) node{\large$\halfP^3_e$};
    \draw ($(O)+(0:\car)$) -- +(90:\car) -- (0,\car);
  \end{tikzpicture}
\end{lrbox}

\newcommand{\schemSubd}{
   \pgfmathsetmacro{\R}{0.7}
    \pgfmathsetmacro{\RR}{1.4}
    \coordinate (A) at (-8,0);
    \coordinate (B) at (3,0);
    \coordinate (B2) at (14,0);

    \coordinate (C) at ($(B)+(0.66,2)$);
    \coordinate (C2) at ($(B)+(2.25,6.75)$);
    \coordinate (D) at ($(C)+(2,2)$);
    \coordinate (D2) at ($(C)+(5,5)$);
    \coordinate (E) at ($(D)+(5,1)$);
    \coordinate (E2) at ($(D)+(8.75,1.75)$);

    \draw (A) -- (B) coordinate[pos=0.5] (AA);
    \draw[dashed] (A) -- ($(A)+(-3,0)$);
    \draw (B) -- (B2) coordinate[pos=0.5] (BB);

    \coordinate (Z) at ($(BB)+(-1.,-3)$);
    \coordinate (Z2) at ($(BB)+(-2.,-6.)$);
    \coordinate (Y) at ($(Z)+(-9,-3)$);
    \coordinate (AAB) at ($(AA)+(-1.5,3.)$);
    \coordinate (AAB2) at ($(AAB)+(-1.5,3.)$);
    \coordinate (AAC) at ($(AAB)+(0,3.5)$);

    \draw[dashed] (B2) -- ($(B2)+(4,0)$);
    \draw (B) -- (C);
    \draw (C) -- (C2);
    \draw[dashed] (C2) -- ($(C2)+(0.5,1.5)$);

    \draw (BB) -- (Z);
    \draw (Z) -- (Z2);
    \draw[dashed] (Z2) -- ($(Z2)+(-0.5,-1.5)$);

}

\newcommand{\elsing}[1]{
  \begin{tikzpicture}[x=0.7cm,y=.7cm]
    \pgfmathsetmacro{\size}{2.5}
    \pgfmathsetmacro{\del}{0.65}
    \pgfmathsetmacro{\pos}{0.55}
    \pgfmathsetmacro{\car}{0.4}

    \coordinate (O) at (0,0);
    \ifnum#1=5

    \else
    \draw (O) node{$\times$}; 
     \draw (O) node[anchor=north, inner sep=1pt]
     {\footnotesize$\varphi^{-1}(p_2)$}; 
     \fi
    \coordinate (A) at (0,\size);
    \coordinate (B) at (\size,0);
    \draw (O) -- (A);
    \draw (O) -- (B);
    \draw[dashed] (B) -- ++(0:\del);
    \draw[dashed] (A) -- ++(90:\del);
    \draw ($(A)!.5!(B)$) node[anchor=south west,inner sep=0pt] {$\halfP_e^{#1}$};
    \draw ($(O)+(0:\car)$) -- +(90:\car) -- (0,\car);
  \end{tikzpicture}
}
\newcommand{\base}{
  \draw (0,0) coordinate (a0) -- +(-60:1) coordinate (a1) 
  node[pos=0.8,anchor=east, inner sep=5pt]{$\eta_1$}
  -- ($(a1)+(-30:1)$) coordinate (a2) -- ($(a2)+(0:1)$) coordinate (a3) 
  -- ($(a3)+(30:1)$) coordinate (a4) -- ($(a4)+(60:1)$) coordinate (a5)
  node[pos=0.,anchor=north west, inner sep=0pt]{$\eta_2$};
  \draw[dotted,thick] (0,0) -- +(120:0.3);
  \draw[dotted,thick] (a5) -- +(60:0.3);
}

\newcommand{\schem}[1]{
  \base
  \draw (a1) -- ($(a1)+(0:1)$) coordinate (bt3) -- ($(bt3)+(30:1)$) coordinate (bt4) 
  -- ($(bt4)+(60:0.7)$) coordinate (bt5);
  \draw (bt3) -- (a3);
  \draw (bt4) -- (a4);
  \draw (bt3) -- ($(bt3)+(a0)-(a1)$) coordinate (az1);
  \draw (bt4) -- ($(bt4)+(a0)-(a1)-(120:0.3)$) coordinate (az2);

  \draw[dotted,thick] (az1) -- +(120:0.3);
  \draw[dotted,thick] (az2) -- +(120:0.3);
  \draw[dotted,thick] (bt5) -- +(60:0.3);
  % \draw (bt5) -- (a5);
  % \end{scope}
  \draw (a2) node[anchor=north east, inner sep=1pt]{$p_2$};
  \draw (a2) node{$\times$};
  % \draw[dotted,thick] (4,0) -- +(120:0.3);
  % \draw[dotted,thick] (a5)++(180:0.55) -- +(60:0.4);

  \ifnum#1=1
  \draw[align=center,decoration={brace,mirror,raise=10pt,amplitude=10pt},decorate]
  ($(a0)+(-160:0.3)$) -- node[below left=17pt] {\small induction\\ on $N_1$} ($(a2)+(-160:0.3)$);
  \draw[align=center,decoration={brace,mirror,raise=20pt,amplitude=10pt},decorate]
  ($(a2)+(-50:0.2)$) -- node[below right=25pt] {\small induction\\ on $N_2$} ($(a5)+(-50:0.2)$);
  \fi
}
\newcommand{\schemd}{
  \schem{0}
  \draw[dotted,thick] ($(az1)!.5!(a0)$) -- +(120:0.3);
  \draw[dotted,thick] ($(az1)!.5!(az2)$) -- +(120:0.3);
  \draw[dotted,thick] ($(bt5)!.5!(az2)$) -- +(90:0.3);
  \draw[dotted,thick] ($(bt5)!.5!(a5)$) -- +(60:0.3);
}

\newcommand{\schema}{
  \base
  \draw (a3) node{$\times$};
  \draw (a3) node[anchor=north, inner sep=2pt]{$p_3$};
  \draw (a2) -- ($(a2)+(30:1)$) coordinate (ct4) -- ($(ct4)+(60:1.)$) coordinate (ct5);
  \draw (ct4) -- (a4);
  \draw[dotted,thick] (ct5) -- +(60:0.3);

%  \draw (ct3) -- ($(ct3)+(a0)-(a1)$) coordinate (az1);
  \draw (a1) -- ($(a1)+(a4)-(a3)$) coordinate (az2);
  \draw (ct4) -- (az2);
  \draw (az2) -- ($(az2)+(a0)-(a1)-(120:.25)$) coordinate (az4);
  \draw[dotted,thick] (az4) -- +(120:0.3);

  \draw (az2) -- ($(az2)+(a5)-(a4)-(60:.25)$) coordinate (az3);
  \draw[dotted,thick] (az3) -- +(60:0.3);
  \draw[dotted,thick] (a5)++(165:0.5) -- +(-120:0.4);

  \draw[dotted,thick] ($(a0)!.5!(az4)$) -- +(120:0.3);
  \draw[dotted,thick] ($(az3)!.5!(az4)$) -- +(90:0.3);
  \draw[dotted,thick] ($(ct5)!.5!(az3)$) -- +(60:0.3);

}

\newcommand{\schemb}{
  \base
  \draw (a1) node{$\times$};
  \draw (a1) node[anchor=north east, inner sep=1pt]{$p_1$};
  \draw[dotted,thick] (a5) -- +(60:0.3);

  \draw (a2) -- ($(a2)+(120:1.5)$) coordinate (az0);
  \draw (a3) -- ($(a3)+(120:1.5)$) coordinate (az1);
  \draw (a4) -- ($(a4)+(120:1.1)$) coordinate (az2);
  \draw[dotted,thick] (az0) -- +(120:0.3);
  \draw[dotted,thick] (az1) -- +(120:0.3);
  \draw[dotted,thick] (az2) -- +(120:0.3);

  \draw[dotted,thick] ($(az0)!.5!(az1)$) -- +(120:0.3);
  \draw[dotted,thick] ($(az1)!.5!(az2)$) -- +(120:0.3);
  \draw[dotted,thick] ($(a0)!.5!(az0)$) -- +(120:0.3);
  \draw[dotted,thick] ($(a5)!.5!(az2)$) -- +(90:0.3);
  % \draw (ht0) -- (a0);

}
\newcommand{\schemc}{
  \draw[dotted,thick] (0,0) -- +(120:0.3);
  \draw (0,0) coordinate (a0) -- +(-60:1) coordinate (a1) -- ($(a1)+(-30:1)$)
  coordinate (a2) -- ($(a2)+(0:1)$) coordinate (a3) 
  node[pos=0.1,anchor=north east, inner sep=2pt]{$\eta_1$} -- ($(a3)+(30:1)$) 
  coordinate (a4) -- ($(a4)+(60:1)$) 
  coordinate (a5) node[pos=0.5,anchor=north west, inner sep=2pt]{$\eta_2$};
  \draw (a4) node{$\times$};
  \draw (a4) node[anchor=north west, inner sep=1pt]{$p_4$};
  \draw[dotted,thick] (a5) -- +(60:0.3);

  \draw (a3)  -- ($(a3)+(60:1.5)$) coordinate (dt5);
  % \draw (dt5) -- (a5);
  \draw (a3)  -- ($(a3)+(60:1.5)$) coordinate (dt1);
  % \draw (dt5) -- (a5);
  \draw (a2)  -- ($(a2)+(60:1.5)$) coordinate (dt2);
  \draw (a1)  -- ($(a1)+(60:1.1)$) coordinate (dt3);
  \draw[dotted,thick] (dt1) -- +(60:0.3);
  \draw[dotted,thick] (dt2) -- +(60:0.3);
  \draw[dotted,thick] (dt3) -- +(60:0.3);
  \draw[dotted,thick] ($(dt1)!.5!(dt2)$) -- +(60:0.3);
  \draw[dotted,thick] ($(dt3)!.5!(dt2)$) -- +(60:0.3);
  \draw[dotted,thick] ($(a0)!.5!(dt3)$) -- +(90:0.3);
  \draw[dotted,thick] ($(a5)!.5!(dt1)$) -- +(60:0.3);

}

\section{Introduction}
We call {\em surface} a Riemannian 2-manifold, whose metric will be denoted $g$, and we consider complete, simply connected surfaces. 
A Chebyshev net $\varphi:U\subset\R^2\to\varphi(U)\subset\surf$, with $U$ an open set, is a coordinate system satisfying
\begin{equation}\label{eq:cheb-def}
  |\DU\varphi|_g(u,v) = |\DV\varphi|_g(u,v) = 1,
\end{equation}
for all $(u,v)\in U$.
We construct in what follows Chebyshev nets with a finite set of conical singularities on surfaces with finite total negative curvature and total positive curvature lower than $2\pi$. The main result of this chapter is the following theorem.
\begin{theorem}[Existence of piecewise smooth Chebyshev nets with singularities]\label{thm:existence-cheb-net}
  Let $\surf$ be a smooth, complete, simply connected surface satisfying
\begin{equation} \label{eq:cond-thm}
  \int_{\surf}K^+<2\pi\quad\text{and}\quad\int_{\surf}K^-<\infty,
\end{equation}
where $K$ is the Gaussian curvature of $\surf$, $K^+=\max(K,0)$ and $K^-=\max(-K,0)$. %We set $N_{\max} = \frac{4}{\pi}\int_\surf K^-+4$.
Then, there exists a piecewise smooth Chebyshev net with conical singularities \sloppy$\CC=\big(\{\halfP^i_e\}_{1\leq i\leq \Npol}, \{\varphi^i_e\}_{1\leq i\leq \Npol}, T)$, with $\Npol\leq \frac{4}{\pi}\int_\surf K^-+8$, on $\surf$.
% $p_1,...,p_{\Nsing}$, with $\Nsing\leq N_{\max}$, of valence $n_1,...,n_{\Nsing}\in\{5,...,N_{\max}+4\}$ on $\surf$.
\end{theorem}
We highlight that the proof of the theorem is constructive. %Then, let us notice that the Chebyshev net with conical singularities constructed in Theorem \ref{thm:existence-cheb-net} induces a bi-Lipschitz mapping from the plane to $\surf$ \cite{Bur05}. As a result, this theorem is optimal for surfaces having a Gaussian curvature with constant sign \cite{Bonk03}.
The chapter is organized as follows. In Section \ref{subsec:Nhalf-surfaces}, we first consider the construction of Chebyshev nets on broken half-surfaces, defined to be half-surfaces with polygonal boundaries. We prove the existence of Chebyshev nets on broken half-surfaces under some condition on their total curvature in Theorem \ref{thm:cheb-half-surface}. Then, we show in Section \ref{subsec:splitting} that we can split surfaces satisfying \eqref{eq:cond-thm} into broken half-surfaces (Theorem \ref{thm:splitting-surf}), each of them satisfying the conditions of Theorem \ref{thm:cheb-half-surface}. Finally, we combine these two results to construct the Chebyshev net with conical singularities in Section \ref{subsec:cheb-net-sing} and we show that this Chebyshev net is piecewise smooth.

Before this, let us introduce some notation. First, unless explicitly mentioned, any curve $\eta:I\subset \R\to\surf$ we consider in what follows is arc-length parametrized, continuous on $I$, and piecewise smooth according to the following definition:
\begin{definitionE}[Piecewise smooth curves]\label{def:piecewise}
  Let $\eta:I\subset \R\to\surf$ be a continuous curve. We say that the curve $\eta$ is \emph{piecewise smooth} if there exists a partition of $I$ in the form $\bigcup_{i=1}^{N+1} [a_{i-1},a_i]=I$, with $a_0<...<a_{N+1}$. Suppose moreover that $\eta$ restricted to $(a_{i-1},a_{i})$ is a smooth curve with all the derivatives having a finite limit from the right at $a_{i-1}$ and from the left at $a_{i}$, for all $i\in\{1,...,N+1\}$. We say that the curve $\eta$ is piecewise smooth.
\end{definitionE}
 We denote $\angle(X,Y)\in(-\pi,\pi]$ the oriented angle (using the orientation of $\surf$) between the vectors $X$ and $Y$ in the tangent plane $T_p\surf$ at any point $p\in\surf$. We define the total positive and negative turn angle of continuous piecewise smooth curves (see \cite{Bur05}):
\begin{definitionE}[Positive and negative turn angle $\tau_\pm$]
 Let $\eta:I\subset\R\to\surf$ be a continuous piecewise smooth curve on the partition of $I$ defined by $a_0<...<a_{N+1}$. Then, for all $i\in\{1,...,N+1\}$, let $\ko_i:[a_{i-1},a_{i}]\to\R$ be the geodesic curvature of $\eta\big|_{[a_{i-1},a_{i}]}$ defined by 
\begin{equation*}
  \ko_i(s) = \langle \eta^{\prime\prime}(s), \eta^{\prime\perp}(s)\rangle_g,
\end{equation*}
with $\eta^{\prime\perp}(s)\in T_{\eta(s)}\surf$ the vector such that $\angle(\eta'(s),\eta^{\prime\perp}(s))=\frac{\pi}{2}$, for all $s\in [a_{i-1},a_{i}]$.
Let $\psi_i = \angle(\eta'(a_i^-),\eta'(a_i^+))$, for all $i\in\{1,...,N\}$. We suppose that $-\pi<\psi_i<\pi$, for all $i\in\{1,...,N\}$. We define the total positive and negative \emph{turn angles} $\tau(\eta)$ by
\begin{equation}\label{eq:int-curv}
\tau_+(\eta) = \sum_{i=1}^{N+1}\int_{a_{i-1}}^{a_{i}}\ko_i^+ + \sum_{i=1}^N\psi_i^+,
\quad \tau_-(\eta) = \sum_{i=1}^{N+1}\int_{a_{i-1}}^{a_{i}}\ko_i^- + \sum_{i=1}^N\psi_i^-,
\end{equation}
and we define the total \emph{turn angle} as $\tau(\eta) = \tau_+(\eta)-\tau_-(\eta)$. (Note that $\tau_{\pm}(\eta)$ are different from $(\tau(\eta))^\pm$.) We denote $\tau\big(\eta\big|_{[a,b]})$, with $a,b\in\R$ such that $a<b$, the restriction to $[a,b]$ of the total turn angle. Note that, if any, the pointwise turns at $a$ and $b$ are included.
\end{definitionE}
An illustration of the turn angle is presented in Figure \ref{fig:turn-angle}. Finally, we denote int($D$) the interior of any set $D$. 
\begin{figure}[!htp]
  \centering
  \begin{tikzpicture}[x=2.cm,y=2.cm]
    \pgfmathsetmacro{\RR}{1.5}
    \pgfmathsetmacro{\del}{.5}
    \pgfmathsetmacro{\th}{30}
    \pgfmathsetmacro{\thh}{130}
    \begin{scope}[rotate=-90]
    \coordinate (A) at (0,0);
    \draw (A) -- ++(\th:\RR+1.) coordinate (B);
    \draw[thick,red,->] (A) -- ++(\th:.3);
    \draw (B) arc[start angle=-40,delta angle=60,radius=1.5] coordinate (C);
    \draw (C) -- ++(\thh:\RR) coordinate (D);
    \draw (D) -- ++(150:\RR) coordinate (E);

    \draw (A) node{$\times$};
    \draw (B) node{$\times$};
    \draw (C) node{$\times$};
    \draw (D) node{$\times$};
    \draw (E) node{$\times$};

    \draw ($(C)+(-110:.4)$) node{\Large$\eta$};

    \draw[thick,red,->] (E) -- ++(150:.3);
    \draw[thick,red,->] (E) -- ++(\th:.3);
    \draw[red,-latex] ($(E)+(\th:.2)$) arc[start angle=\th,delta angle=150-\th,radius=.2];
    \draw[red] ($(E)+(90:.4)$) node{$\tau(\eta)$};

    \draw[dotted,thick] (B) -- ++(-130:\del);
    \draw[latex-] ($(B)+(-130:.4)$) arc[start angle=-130,delta angle=-20,radius=.4];
    \draw ($(B)+(-140:.56)$) node{$\psi_1$};
